\textsc{Remarks on the vanishing viscosity process of state-constraint Hamilton--Jacobi equations}

### 2021-07-15 Drafts and notes/Draft_07.tex
Almost final

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
    \def\svgwidth{\columnwidth}
    \import{./figs/}{#1.pdf_tex}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title[Rate of convergence]
{\textsc{Remarks on the vanishing viscosity process of state-constraint Hamilton--Jacobi equations}}
\thanks{The authors are supported in part by NSF grant DMS-1664424 and NSF CAREER grant DMS-1843320. The work of Son N. T. Tu is supported in part by the GSSC Fellowship, University of Wisconsin--Madison.}
\begin{abstract}
We investigate the convergence rate in the vanishing viscosity process of  the solution to the state-constraint Hamilton-Jacobi equation. We show by a simple proof that for Lipschitz data that vanish on the boundary, the rate of convergence is $\mathcal{O}(\sqrt{\varepsilon})$ with a specific boundary layer. Moreover, the rate can be improved to $\mathcal{O}(\varepsilon)$ in the region with zero data. The proof relies on the doubling variable method and the construction of a specific barrier.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Yuxi Han}
\address[Y. Han]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{yuxi.han@wisc.edu}
\author{Son N. T. Tu}
\address[S. N.T. Tu]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{thaison@math.wisc.edu}
\date{\today}
\keywords{first-order Hamilton--Jacobi equations; second-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions.}
\subjclass[2010]{
35B40, %Asymptotic behavior of solutions, 
35D40, %Viscosity solutions
49J20, %Optimal control problems involving partial differential equations
49L25, %Viscosity solutions
70H20 %Hamilton-Jacobi equations
}
\maketitle
\setcounter{tocdepth}{1}
%\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\subsection{Settings} Let $\Omega$ be an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$. Let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
 \begin{equation}\label{eq:PDEepsa}
      u^\varepsilon(x) + H(Du^\varepsilon(x)) - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty
 where $H:\R^n\to\R^n$ is a continuous Hamiltonian. Solution that blows up uniformly on the boundary is also called \emph{large solution}. A typical subquadratic Hamiltonian that has been considered in the literature is $H(\xi) = |\xi|^p$ for $\xi\in \R^n$ where $1<p\leq 2$. We focus on this Hamiltonian in our paper, and the equation of interest becomes
\begin{equation}\label{eq:PDEeps}
      u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
    \end{cases} \tag{PDE$_\varepsilon$}
When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the value function associated with a minimization problem in stochastic optimal control with state constraint (\cite{Lasry1989}). We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0^+$. Heuristically, the solution of the second-order state-constraint problem converges to that of a first-order state-constraint problem associated with the deterministic optimal control, namely,
\begin{equation}\label{eq:PDE0}
       u(x) + |Du(x)|^p - f(x) \leq 0\;\qquad\text{in}\;\Omega,\\
       u(x) + |Du(x)|^p - f(x) \geq 0\;\qquad\text{on}\;\overline{\Omega},
    \end{cases} \tag{PDE$_0$}
as is described in the framework of viscosity solution.
Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all the viscosity subsolutions in $\rmC(\overline{\Omega})$(see \cite{Capuzzo-Dolcetta1990,Soner1986}). The problem is interesting since in the limit we no longer have blowing up behavior. In this paper, we investigate the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0^+$. What is intriguing and delicate here is the narrow boundary layer behavior near $\partial \Omega$.
\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary satisfying either %$H:\mathbb{R}^n\times \mathbb{R}^n$ is a continuous Hamiltonian. 
%\begin{itemize}
%    \item[$\mathrm{(A1)}$] $H(x,\varrho) = |\varrho|^p - f(x)$ where $1<p\leq 2$ and $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$.
%\end{itemize}
%    The following assumptions on $\Omega$ will also be used.
    \item[(A1)] There exists a universal pair of positive numbers $(r,h)$ and $\eta\in \mathrm{BUC}(\overline{\Omega};\mathbb{R}^n)$ such that $B(x+t\eta(x), rt)\subset\Omega$ for all $t\in (0,h]$,
    or
    \item[(A2)] $\Omega$ is a bounded star-shaped (with respect to the origin) open subset of $\mathbb{R}^n$ such that for some $\kappa > 0$,
        \mathrm{dist}(x,\overline{\Omega}) \geq \kappa r \qquad\text{for all}\; x\in (1+r) \partial\Omega, \;\text{for all}\;r>0.
Equation \eqref{eq:PDEeps} follows the setting of \cite{Lasry1989}, where the specific structure of the Hamiltonian $H(x,\xi) = |\xi|^p - f(x)$ enables more explicit estimates for the solution of \eqref{eq:PDEeps}. Assumption $\mathrm{(A1)}$ or $\mathrm{(A2)}$ guarantees that a comparison principle holds for the state-constraint problem \eqref{eq:PDE0}. Assumption $\mathrm{(A1)}$, which holds for any smooth bounded domain, was first studied in \cite{Soner1986}. Assumption $\mathrm{(A2)}$ was posed and studied in \cite{Capuzzo-Dolcetta1990}. 
%We list the assumptions on a general Hamiltonian as follow.
%\begin{itemize}
%    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
%    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
%    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
%    \begin{equation*}
%        \begin{cases}
%        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
%        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
%        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
%    \end{equation*}
%    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
%\end{itemize}

\subsection{Relevant literature} There is a
vast amount of work in the literature on large solutions and second-order viscosity solutions with state constraints. The problem \eqref{eq:PDEeps} is first studied in \cite{Lasry1989} and subsequently many works have been done in understanding deeper the properties of solutions. %For instance, \textcolor{red}{(more references here.)}. 
We refer the readers to \cite{ Porretta_a,alessio_asymptotic_2006,Bandle_1994, marcus_existence_2003} and the references therein. The time-dependent version of \eqref{eq:PDEepsa} is also studied by many works, for instance \cite{barles_generalized_2004,barles_large_2010,leonori_local_2011,moll_large_2012} and the references therein.

In terms of rate of convergence, up to our knowledge such a question has not been studied in the literature. For the case \eqref{eq:PDEeps} is equipped with the Dirichlet boundary condition, a rate $\mathcal{O}(\sqrt{\varepsilon})$ is well known with multiple proofs (see \cite{Bardi1997,crandall1984, tran_hamilton-jacobi_2021}). We believe part of the reason why the problem is intriguing is that the blowing up behavior of the solution is complicated and deserves further investigation.

\subsection{Main results} The main result of the paper is the following theorem.

\begin{thm}\label{main_thm1} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume that $1 < p\leq 2$ and $f$ is Lipschitz with $f = 0$ on $\partial\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ such that for $x\in \Omega$,
\begin{align*}
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
\end{align*}
\end{thm}

\begin{rem} To the best of our knowledge, this theorem is new in the literature. We don't know if the order of $\varepsilon$ on the right hand side of the inequalities above is optimal or not near the boundary and this deserves further investigation. The condition $f = 0$ on $\partial\Omega$ is a little bit restrictive but can be explained as follows. One can see that the solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}). If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a convergence rate of $u^\varepsilon-u$ is easier to obtain. Indeed, using the usual doubling variable technique, it is natural to consider the doubling variable for
\begin{equation}\label{heur1}
    u^\varepsilon(x) - \frac{C\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
\end{equation}
and $u(x)$, where $C\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $\mathrm{dist}(x,\partial\Omega)\to 0$. After taking derivative, heuristically, \eqref{heur1} becomes
\begin{equation}\label{heur2}
    Du^\varepsilon(x) + C\alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x).
\end{equation}
We show in Lemma \ref{lem:boundDu^eps} that \eqref{heur2} gives the correct behavior of $Du^\varepsilon$ where $\alpha = \frac{2-p}{p-1}$. \\
\noindent
\textcolor{blue}{
To get a useful estimate by the doubling variable, at the maximum point $x_0$ of $u^\varepsilon(x) - u(x)$, we must have $d(x_0)\approx \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0$. It turns out that such an estimate is quite delicate. We overcome this difficulty by decomposing the solution into an inside part and an outside part near the boundary, where we have reduced to the case of $f=0$.}
\end{rem}

Using the convexity of $|\xi|^p$, we can avoid the doubling variable route to get a better one-sided estimate for compactly supported $f$. Such an one-sided rate is well-known for the case of vanishing discount with zero Dirichlet boundary condition (see \textcolor{blue}{NEED CITATION}).

\begin{thm}\label{main_thm2} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume that $1 < p\leq 2$ and $f$ is a compactly supported Lipschitz function defined on $\overline{\Omega}$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ such that for $x\in \Omega$,
\begin{align*}
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq  \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
\end{align*}
\end{thm}

\subsection*{Organization of the paper} In Section 2, we state some preliminary results. In Section 3, we prove the main result on the rate of convergence. The proofs of some lemmas are presented in Appendix.

\section{Preliminaries}\label{sec:prelim} 
\subsection{Setting and simplifications} Let $\Omega$ be an open, bounded and connected subset of $\mathbb{R}^n$ with boundary $\partial\Omega$ of class $C^2$. For small $\delta>0$, we denote $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) > \delta\}$ and $\Omega^\delta = \{x\in \mathbb{R}^n: \mathrm{dist}(x,\overline{\Omega}) < \delta\}$. 
\begin{figure}[ht]
    \centering
    %\incfig{Domains}
    \def\svgwidth{0.35\columnwidth}
    \import{./figs/}{Domains.pdf_tex}
    \caption{The domain $\Omega$ and its variations $\Omega_\delta, \Omega^\delta$.}
    \label{fig:Domains}
\end{figure}

\begin{defn} Define
\begin{equation}\label{def:delta_0}
    \delta_{0,\Omega} =\frac{1}{2}\sup \big\{ \delta > 0: x\mapsto\mathrm{dist}(x,\partial\Omega)\;\text{is}\;\rmC^2\;\text{in}\;\Omega\backslash\overline{\Omega}_{\delta} \big\}.
\end{equation}
%The distance function is of class $\mathrm{C}^2$ in the region where $0<\mathrm{dist}(x,\partial\Omega) < \delta_0$. 
We will simply write $\delta_0$ instead of $\delta_{0,\Omega}$ if the underlying domain is understood.
\end{defn}

We refer the reader to \cite{gilbarg_elliptic_2001} for the regularity of the distance function defined in the definition above. We then extend $\mathrm{dist}(x,\partial\Omega)$ to a function $d(x)\in \mathrm{C}^2(\mathbb{R}^n)$ such that 
\begin{equation}\label{e:distance_def}
    \begin{cases}
    d(x)\geq 0\;\text{for}\;x\in\Omega\;\text{with}\;d(x) = +\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega\backslash \Omega_{\delta_0},\\
    d(x)\leq 0\;\text{for}\;x\notin \Omega\;\text{with}\;d(x) = -\mathrm{dist}(x,\partial\Omega)\;\text{for}\;x\in \Omega^{\delta_0}\backslash \Omega.
    \end{cases}
\end{equation}
Note that $|D d(x)| = 1$ in the viscosity sense (and thus in classical sense) in $\Omega^{\delta_0}\backslash \Omega_{\delta_0}$. Let 
\begin{equation}\label{boundond}
   K_0:= \max_{x\in \overline{\Omega}}|d(x)|, \qquad K_1 := \max_{x\in \overline{\Omega}} |D d(x)| \qquad\text{and}\qquad K_2 := \max_{x\in \overline{\Omega}} |\Delta d(x)|.
\end{equation}
\noindent Denote by $\mathcal{L}^\varepsilon:\rmC^2(\Omega)\to \rmC(\Omega)$ the operator
\begin{equation*}
    \mathcal{L}^\varepsilon[u](x) :=   u(x) + |Du(x)|^p - f(x) - \varepsilon \Delta u(x), \qquad x\in \Omega.
\end{equation*}

\subsection{Local gradient estimate} Let $\Omega$ be an open, bounded subset of $\R^n$, $\varepsilon \in (0,1)$ and $p>1$. We state a priori estimate for $\rmC^2$ solutions of \eqref{eq:PDEeps} (\cite[Appendix]{Lasry1989}). Since we are working with nice solutions, the proof is relatively simple using the classical Bernstein method (\cite{bernstein_sur_1910}). We provide a proof in Appendix for the readers' convenience.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
    \def\svgwidth{\columnwidth}
    \import{./figs/}{#1.pdf_tex}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title[Rate of convergence]
{\textsc{Remarks on the vanishing viscosity process of state-constraint Hamilton--Jacobi equations}}
\thanks{The authors are supported in part by NSF grant DMS-1664424 and NSF CAREER grant DMS-1843320. The work of Son N. T. Tu is supported in part by the GSSC Fellowship, University of Wisconsin--Madison.}
\begin{abstract}
We investigate the convergence rate in the vanishing viscosity process of the solutions to the state-constraint Hamilton-Jacobi equations. We give two different proofs of the fact that, for Lipschitz data that vanish on the boundary, the rate of convergence is $\mathcal{O}(\sqrt{\varepsilon})$ in the interior. Moreover, the one-sided rate can be improved to $\mathcal{O}(\varepsilon)$ for compactly supported data. Our approach relies on deep understanding of the blow-up behavior near the boundary and semiconcavity of the solutions.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Yuxi Han}
\address[Y. Han]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{yuxi.han@wisc.edu}
\author{Son N. T. Tu}
\address[S. N.T. Tu]
{
Department of Mathematics, 
University of Wisconsin Madison, 480 Lincoln  Drive, Madison, WI 53706, USA}
\email{thaison@math.wisc.edu}
\date{\today}
\keywords{first-order Hamilton--Jacobi equations; second-order Hamilton--Jacobi equations; state-constraint problems; optimal control theory; rate of convergence; viscosity solutions; semiconcavity; boundary layer.}
\subjclass[2010]{
35B40, %Asymptotic behavior of solutions, 
35D40, %Viscosity solutions
49J20, %Optimal control problems involving partial differential equations
49L25, %Viscosity solutions
70H20 %Hamilton-Jacobi equations
}
\maketitle
\setcounter{tocdepth}{1}
%\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\subsection{Settings} Let $\Omega$ be an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary, $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$. For $\varepsilon>0$, let $u^\varepsilon\in \mathrm{C}^2(\Omega)$ (see \cite{Lasry1989}) be the solution to
 \begin{equation}\label{eq:PDEepsa}
    \begin{cases}
      u^\varepsilon(x) + H(Du^\varepsilon(x)) - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty
    \end{cases} 
\end{equation}
 where $H:\R^n\to\R^n$ is a given continuous Hamiltonian. The solution that blows up uniformly on the boundary is also called a \emph{large solution}. A typical subquadratic Hamiltonian that has been considered in the literature is $H(\xi) = |\xi|^p$ for $\xi\in \R^n$ where $1<p\leq 2$. We focus on this Hamiltonian in our paper, and the equation of interest becomes
\begin{equation}\label{eq:PDEeps}
    \begin{cases}
      u^\varepsilon(x) + |Du^\varepsilon(x)|^p - f(x) - \varepsilon \Delta u^\varepsilon(x) = 0 \qquad
    \text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^\varepsilon(x) = +\infty.
    \end{cases} \tag{PDE$_\varepsilon$}
\end{equation}
When $1<p\leq 2$, equation \eqref{eq:PDEeps} describes the value function associated with a minimization problem in stochastic optimal control with state constraint (\cite{fabbri_stochastic_2017, Lasry1989}. We are interested in studying the asymptotic behavior of $\{u^\varepsilon\}_{\varepsilon>0}$ as $\varepsilon\rightarrow 0^+$. Heuristically, the solution of the second-order state-constraint problem converges to that of a first-order state-constraint problem associated with the deterministic optimal control, namely,
\begin{equation}\label{eq:PDE0}
    \begin{cases}
       u(x) + |Du(x)|^p - f(x) \leq 0\;\qquad\text{in}\;\Omega,\\
       u(x) + |Du(x)|^p - f(x) \geq 0\;\qquad\text{on}\;\overline{\Omega},
    \end{cases} \tag{PDE$_0$}
\end{equation}
as is described in the framework of the theory of viscosity solutions. Equation \eqref{eq:PDE0} admits a unique viscosity solution in the space $\rmC(\overline{\Omega})$, which is also the maximal viscosity subsolution among all the viscosity subsolutions in $\rmC(\overline{\Omega})$(see \cite{Capuzzo-Dolcetta1990,Soner1986}). The problem is interesting since in the limit we no longer have blowing up behavior. In this paper, we investigate the rate of convergence of $u^\varepsilon \to u$ as $\varepsilon\to 0^+$. What is intriguing and delicate here is the blow-up behavior of $u^\varepsilon$ in a narrow strip near $\partial \Omega$ as $\varepsilon\to 0^+$. This is often called the boundary layer theory in the literature.

Note that a comparison principle holds for \eqref{eq:PDE0} since we always assume $\Omega$ is an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary (\cite{Capuzzo-Dolcetta1990,Soner1986}). Equation \eqref{eq:PDEeps} follows the setting of \cite{Lasry1989}, where the specific structure of the Hamiltonian $H(x,\xi) = |\xi|^p - f(x)$ enables more explicit estimates for the solution of \eqref{eq:PDEeps}.

%\subsection{Assumptions} We will always assume $\Omega$ is an open, bounded and connected domain in $\mathbb{R}^n$ with $\mathrm{C}^2$ boundary. Essentially the domain is assumed so that a comparison principle holds for \eqref{eq:PDE0}.

%\begin{itemize}    
%    \item[(A1)] There exists a universal pair of positive numbers $(r,h)$ and $\eta\in \mathrm{BUC}(\overline{\Omega};\mathbb{R}^n)$ such that $B(x+t\eta(x), rt)\subset\Omega$ for all $t\in (0,h]$,
%    \end{itemize}
%    or
%    \begin{itemize}
%    \item[(A2)] $\Omega$ is a bounded star-shaped (with respect to the origin) open subset of $\mathbb{R}^n$ such that for some $\kappa > 0$,
%    \begin{equation*}
%        \mathrm{dist}(x,\overline{\Omega}) \geq \kappa r \qquad\text{for all}\; x\in (1+r) \partial\Omega, \;\text{for all}\;r>0.
%    \end{equation*}
%\end{itemize}

 %Assumption $\mathrm{(A1)}$ or $\mathrm{(A2)}$ guarantees that a comparison principle holds for the state-constraint problem \eqref{eq:PDE0}. Assumption $\mathrm{(A1)}$, which holds for any smooth bounded domain, was first studied in \cite{Soner1986}. Assumption $\mathrm{(A2)}$ was posed and studied in \cite{Capuzzo-Dolcetta1990} and the references therein. 
%We list the assumptions on a general Hamiltonian as follow.
%\begin{itemize}
%    \item[$\mathrm{(H1)}$] There exists $C_1 > 0$ such that $H(x,p) \geq -C_1$ for all $(x,p)\in \overline{\Omega}\times\mathbb{R}^n$.
%    \item[$\mathrm{(H2)}$] There exists $C_2>0$ such that $|H(x,0)|\,\leq \,C_2$ for all $(x,p)\in \overline{\Omega}\times \mathbb{R}^n$.
%    \item[$\mathrm{(H3)}$] For each $R>0$ there exists a modulus $\omega_{R}[0,\infty)\to [0,\infty)$ such that $\omega_R(0^+) = 0$ and 
%    \begin{equation*}
%        \begin{cases}
%        |H(x,p) - H(y,p)| \leq \omega_R(|x-y|),\\
%        |H(x,p) - H(x,q)| \leq \omega_R(|p-q|),
%        \end{cases} \qquad\text{for all}\;x,y\in \overline{\Omega}, p,q \in \mathbb{R}^n\;\text{with}\;|p|,|q|\leq R.
%    \end{equation*}
%    \item[$\mathrm{(H4)}$] $H(x,p)\rightarrow \infty$ as $|p|\to \infty$ uniformly in $x\in \overline{\Omega}$.
%\end{itemize}

\subsection{Relevant literature} There is a
vast amount of work in the literature on viscosity solutions with state constraints and large solutions. We would like to first mention that the problem \eqref{eq:PDE0} with general Hamiltonian is a huge subject of research interest, started with the pioneer work \cite{Soner1986} (see also \cite{ishii_new_1996,ishii_class_2002}).  Some of the recent work related to the asymptotic behavior of solutions of \eqref{eq:PDE0} can be found in \cite{ishii_vanishing_2017,kim_state-constraint_2020,mitake_asymptotic_2008,tu2021vanishing}. The problem \eqref{eq:PDEeps} is first studied in \cite{Lasry1989} and subsequently many works have been done in understanding deeper the properties of solutions (see \cite{ Porretta_a,alessio_asymptotic_2006,Bandle_1994, marcus_existence_2003} and the references therein). The time-dependent version of \eqref{eq:PDEepsa} is also studied by many works, for instance, \cite{barles_generalized_2004,barles_large_2010,leonori_local_2011,moll_large_2012} and the references therein. %For deterministic and stochastic optimal control problems with state constraints, we refer the read to [\textcolor{blue}{NEED CITATION (Ishii, \cite{}}] and the references therein.

In terms of rate of convergence, that is, the convergence rate of $u^\varepsilon\to u$ as $\varepsilon\to 0^+$, to the best of our knowledge, such a question has not been studied in the literature. For the case where \eqref{eq:PDEeps} is equipped with the Dirichlet boundary condition, a rate $\mathcal{O}(\sqrt{\varepsilon})$ is well known with multiple proofs (see \cite{Bardi1997,crandall1984, tran_hamilton-jacobi_2021}). We believe part of the reason why the problem is intriguing is that the blow-up behavior of the solutions near the boundary of $\Omega$ is complicated and deserves further investigation.

\subsection{Main results} The main results of the paper are the following theorems.

\begin{thm}\label{main_thm1} Let $\Omega$ be an open, bounded and connected subset of $\R^n$ with $\mathrm{C}^2$ boundary. Assume that $1 < p\leq 2$ and $f$ is Lipschitz with $f = 0$ on $\partial\Omega$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ independent of $\varepsilon\in (0,1)$ such that for $x\in \Omega$,
\begin{align*}
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + C\varepsilon \left(\frac{\varepsilon}{d(x)}\right)^{\frac{2-p}{p-1}} &\qquad\text{if}\; p < 2,\\
    &-C\sqrt{\varepsilon}\leq  u^\varepsilon(x) - u(x)\leq C\sqrt{\varepsilon} + \varepsilon|\log(d(x))| &\qquad\text{if}\; p = 2.
\end{align*}
\end{thm}

\begin{rem} To the best of our knowledge, this theorem is new in the literature. We don't know if the order of $\varepsilon$ on the right hand side of the inequalities above is optimal or not near the boundary and this deserves further investigation. The condition $f = 0$ on $\partial\Omega$ is a little bit restrictive but can be explained as follows. One can see that the solution to \eqref{eq:PDEeps} is continuous with respect to data $f$ in the weak$^*$ topology of $L^\infty(\Omega)$ (see \cite{Lasry1989}). If $f = 0$ on $\partial\Omega$, we are able to approximate $f$ \emph{uniformly} in $L^\infty(\Omega)$ by a sequence of compactly supported functions, where a convergence rate of $u^\varepsilon-u$ is easier to obtain. Indeed, it is natural to consider the doubling variable method with
\begin{equation}\label{heur1}
    \psi^\varepsilon(x) =  u^\varepsilon(x) - \frac{C_\alpha\varepsilon^{\alpha+1}}{d(x)^{\alpha}}
\end{equation}
and $u(x)$, where $d(x)$ is a $\mathrm{C}^2$ extension of the distance function $\mathrm{dist}(x,\partial\Omega)$, $\alpha = (2-p)/(p-1)$ and $C_\alpha\varepsilon^{\alpha+1}d(x)^{-\alpha}$ is the leading order term in the asymptotic expansion of $u^\varepsilon(x)$ as $d(x) \to 0^{+}$. If we take the derivative of \eqref{heur1} formally, it becomes
\begin{equation}\label{heur2}
    D\psi^\varepsilon(x) =  Du^\varepsilon(x) + C_\alpha\alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x).
\end{equation}
We will see that $D\psi^\varepsilon(x)$ is uniformly bounded if $d(x)\geq \varepsilon$ (Lemma \ref{lem:boundDu^eps}). Indeed, 
\begin{equation*}
    -C_\alpha \alpha \left(\frac{\varepsilon}{d(x)}\right)^{\alpha+1}Dd(x)    
\end{equation*}
is more or less the leading order term in the asymptotic expansion of $Du^\varepsilon$ near $\partial\Omega$. Heuristically, this means that the boundary layer is $\mathcal{O}(\varepsilon)$ from the boundary.

However, to get a useful estimate by the doubling variable, at the maximum point $x_0$ of $\psi^\varepsilon(x) - u(x)$, we need to have $d(x_0)\geq \varepsilon^{\gamma}$ for $\gamma<1$ so that the latter term in \eqref{heur2} vanishes as $\varepsilon\to 0^+$. In the other case where $d(x_0) < \varepsilon^{\gamma}$, we introduce a new localization idea, that is, we construct a blow-up solution in the ball of radius $\varepsilon^\gamma$ from the boundary. Finally, a technical (and common for the doubling variable) computation leads to $\gamma = 1/2$.

%Essentially we avoid the boundary layer here.

%In the complicated case that $x_0$ is in the boundary layer, we introduce a new localization idea, that is, we construct a blow-up solution in the ball of radius $\varepsilon$.
%\textcolor{red}{(Actually, I am thinking should it be the ball of radius $\sqrt{\varepsilon}$ from the boundary? Since we choose $\kappa=\sqrt{\varepsilon}$.)}
\end{rem}

As a different approach, the convexity of $|\xi|^p$ and the semiconcavity of the solution to \eqref{eq:PDE0} give us a better one-sided $\mathcal{O}(\varepsilon)$ estimate for compactly supported $f$. Such an one-sided $\mathcal{O}(\varepsilon)$ rate is well known for the case of the Dirichlet boundary problem (see \cite{Bardi1997,tran_hamilton-jacobi_2021}). Moreover, this approach provides us with a new proof of the $\mathcal{O}(\sqrt{\varepsilon})$ rate in Theorem \ref{main_thm1} without using the doubling variable method.

%As a different approach, if we utilize the convexity of $|\xi|^p$ and the semiconcavity of the solution to \eqref{eq:PDE0} then we have a proof of the $\mathcal{O}(\sqrt{\varepsilon})$ rate without using the doubling variable method. More importantly, this approach gives a better one-sided $\mathcal{O}(\varepsilon)$ estimate for compactly supported $f$. Such an one-sided $\mathcal{O}(\varepsilon)$ rate is well known for the case of Dirichlet boundary problem (see \cite{Bardi1997,tran_hamilton-jacobi_2021}).

\begin{thm}[One-sided $\mathcal{O}(\varepsilon)$ rate for compactly supported data]\label{thm:rate_doubling2} Assume that $f\in \mathrm{C}^2_c(\Omega)$ such that $\mathrm{supp}(f)\subset\Omega_\kappa$ where  $\Omega_\kappa := \{x\in \Omega: \mathrm{dist}(x,\Omega) > \kappa\}$ for some fixed $\kappa \in (0, \delta_{0})$. Let $u^\varepsilon$ be the unique solution to \eqref{eq:PDEeps} and $u$ be the unique solution to \eqref{eq:PDE0}. Then there exists a constant $C$ independent of $\varepsilon$ and $\kappa$ such that
\begin{equation*}
\begin{aligned}
    u^\varepsilon(x) - u(x) &\leq\frac{\nu C_\alpha \varepsilon^{\alpha+1}}{d(x)^\alpha} + C\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} \left(1+ \left(\frac{\varepsilon}{\kappa}\right) +\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+1} +\left(\frac{\varepsilon}{\kappa}\right)^{\alpha+2}\right) + nc\varepsilon,  &\quad p <2, \\
    u^\varepsilon(x) - u(x) & \leq \nu \varepsilon \log\left( \frac{1}{d(x)}\right)+C\left(\frac{\varepsilon}{\kappa}\right) \left(1+\frac{\varepsilon}{\kappa}\right)+ nc \varepsilon, &\quad p=2.
\end{aligned}
\end{equation*}
where $c = \max \big\lbrace  D_{\xi\xi}f(x): |\xi|=1, x\in \overline{\Omega} \big\rbrace\geq 0$.
\end{thm}
